### 2013-04-01 doc/final_report/implementation.tex
Finished first draft of implementation chapter

@@

In order to provide a useful service to researchers looking for papers, growing
a large corpus of scientific literature was made a high priority during the
project. This was especially important when training the Machine Learning
models since training data sets need to be statistically significant in order
to provide any meaninful results. Users are given the option, and actively
encouraged, to upload papers that they own or publish on another author's
behalf to the Partridge instance. However, to speed up this process, a number
of papers were acquired from various open access sources.

@@

Whilst these libraries did not provide any assistance specific to the domains
of information retrieval or machine learning, they did help accelerate the
design of the frontend interfaces and provide cross-browser compatible HTML5
interfaces. Other javascript libraries providing multiple file upload
capability and browser history manipulation were incorporated into specific
user interface modules.

@@

@@

@@

The system is implemented as a standard web page wrapped inside a javascript
bootstrap module that can be added as a bookmark to a user's web browser. When
the user finds a paper that they wish to add to Partridge on one of the
compatible journal sites, they click the bookmark, loading an embedded frame in
their current browser window and automatically uploading the paper that the
user is looking at to Partridge's server.

The bookmarklet trivialises the act of adding new papers to Partridge and this
should help to encourage users to help grow Partridge's paper corpus.

>>>>

Several libraries were used to accelerate the development and implementation of
Partridge and avoid `reinventing the wheel.' Whenever code libraries were used,
the role of the engineer was to be aware of the available solutions and deduce
which was aposite to the purpose intended.

@@

In order to provide a useful service to researchers looking for papers, growing
a large corpus of scientific literature was made a high priority during the
project. This was especially important when training the Machine Learning
models since training data sets need to be statistically significant in order
to provide any meaningful results. Users are given the option, and actively
encouraged, to upload papers that they own or publish on another author's
behalf to the Partridge instance. However, to speed up this process, a number
of papers were acquired from various open access sources.

@@

Whilst these libraries did not provide any assistance specific to the domains
of information retrieval or machine learning, they did help accelerate the
implementation of the frontend interfaces and provide cross-browser compatible HTML5
interfaces. Other javascript libraries providing multiple file upload
capability and browser history manipulation were incorporated into specific
user interface modules.

@@

After the project had been running for approximately 1 iteration, it was
decided that the query and results views were confusing and provided a
disjointed user experience for those trying to query the system. The results
view was initially designed as a separate page to the query view and
consequentially, users found it quite confusing when trying to relate the
results from the system to the query they had provided on the previous page and
it was inconvenient to have to keep changing the page when manipulating the
query.

To improve the Partridge user experience, the query and results views were
combined into a single interactive page that used JavaScript to retrieve
results from the backend system and simply append them to the current page
using a jQuery function.

\begin{figure}[!h]
\centering
\includegraphics[width=\textwidth]{images/implementation/queryform_actual.png}
\caption{The updated query form with integrated results}
\label{fig:queryform_actual}
\end{figure}

The redesigned query form, as shown in Figure \ref{fig:queryform_actual},
allows the user to add constraints to the query one at a time using the input
field at the top of the page. These constraints are then listed on the left
hand side and can be removed by clicking on the relevant cross icon next to the
term to be removed. Filters such as paper type and topic are available in the
left toolbar and be manipulating using the relevant dropdown box. Changing any
of the filters or constraints automatically triggers the JavaScript routine to
retrieve new results from the server.

Using JavaScript to update the results and manage the query on a single page
provides a significantly better user experience. Unfortunately, it does
interfere with how browser handle a user's history, breaking the Back and
Forward buttons in all browsers and preventing users from linking to their
query results and posting them to friends or colleagues.

The jQuery BBQ (jqBBQ) library was used to restore this functionality
\cite{jqbbq2013}. The library allows the scripted manipulation of the URI
fragment, a string that forms part of a page's URI but does not change the HTTP
request made to the server\cite{urifragment2013}. The fragment can be used to
serialise the the state of the user interface, allowing users to share links to
search results and restoring browser history functionality. A javascript
function was set up to fire when the interface was fully loaded and examine the
URL fragment, converting key, value pairs into search constraints. A
serialisation function was also set up to trigger whenever search constraints
and filters were added and removed from the query and update the fragment
string accordingly.

@@

The paper upload interface was initially designed to allow authors of papers to
submit their work to be analysed by Partridge and display the upload progress
in the form of a horizontal progress bar on the page. Normally, web browsers
only allow the selection of one file at a time for upload and makes an HTTP
request with the file data, without telling the user how long it might take or
providing any information on the upload progress. To implement multiple file
uploads and a progress bar, a significant amount of JavaScript code is
required.

jQuery HTML5 Upload was used to speed up implementing this feature. This
library provides an interface for uploading files asynchronously within the
user's web browser and triggering a callback method when progress is made
during an upload and when a file ha finished uploading. This allowed the
implementation of a progress bar and text readout of the upload progress
without forcing the browser to refresh the page.

After reviewing the design of the page, a new checkbox was added to the upload
form that forces the user to verify that they have permission to upload the
paper in an attempt to prevent problems with copyright and ownership issues.
The users are also linked to \url{http://www.sherpa.ac.uk/romeo/}, a service
that can be used to identify the copyright policy of paper authors and
journals and whether specific papers can be used by Partridge.

@@

The system is implemented as a standard web page wrapped inside a JavaScript
module that can be added as a bookmark to a user's web browser. When the user
finds a paper that they wish to add to Partridge on one of the compatible
journal sites, they click the bookmark, loading an embedded frame in their
current browser window and automatically uploading the paper that the user is
looking at to Partridge's server.

The bookmarklet trivialises the act of adding new papers to Partridge and this
should help to encourage users to help grow Partridge's paper corpus as quickly
as possible. It should also remove complications surrouding the rights of authors and
publishers of papers since it is only compatible with sites that publish open
access articles and cannot be used to add papers to Partridge that may be
copyright protected.

\section{Summary}

Partridge's implementation took place over a period of many weeks, with
incremental improvements, often stemming from user suggestions, being
incorporated throughout. There were several deviations from the original
project designs. Nonetheless, most of the designs were appropriate and provided
an excellent starting point for implementation of the project.

The effective and appropriate use of libraries within Partridge helped in
speeding up the development of the project using well tested and maintained
code from other developers. This required a different skillset which could be
considered equally or more important than just writing new code
\emph{vis-à-vis} a holistic understanding of the nature of the project and the
relationships of the core modules. Working with libraries requires
comprehensive conceptualisation of the task at hand whereas programming
requires focus on a specific subset of the component's behaviour and attaining
expected outputs for given inputs to the routine under construction.

### 2013-04-01 doc/final_report/testing.tex
Finished paper preprocessing section in testing and started writing stuff for web backend
Finished first draft of implementation chapter

%introduction to testing
Throughout the implementation of the project, testing has remained a very
important aspect of Partridge's development. A number of testing techniques
have been used in order to evaluate the individual behaviours of Partridge's
key components both separately and the system as a whole. This chapter
discusses the techniques used to test Partridge, the results from these tests
and any implications that these results have had upon development of the
project. Combining all of these testing and evaluation techniques provides an
in depth view of how useful Partridge is and how it can be improved upon.

@@

\section{ Evaluating Learning Algorithms }

>>>>

%introduction to testing
Throughout the implementation of the project, verifying that systems provide
predictable and reliable outputs for given inputs has remained a very important
routine, necessary in Partridge's development. A number of testing techniques
have been used in order to evaluate the individual behaviours of Partridge's
key components both separately and the system as a whole. This chapter
discusses the techniques used to test Partridge, the results from these tests
and any implications that these results have had upon development of the
project. Combining all of these testing and evaluation techniques provides an
in depth view of how useful Partridge is and how it can be improved upon.

@@

\section{ Evaluating Learning Algorithms }
\label{sec:evaluation_learners}
